proportion_of_importance_per_annotation

### 2019-07-01 Scripts/comparing_tfbs_specific_models_with_all_annotations.Rmd
editted script for figure

#GM12878
ggplot(all_rfperfs_mcc[which(all_rfperfs_mcc$CL=="GM12878"),], aes(x=Resolution, y=MCC, group=Annotation, fill=Annotation)) +
  geom_bar(stat="identity", position = position_dodge()) +
  geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,
                 position=position_dodge(.9), alpha=0.75) +
  theme_minimal() +
  theme_bw()+
  #xlab("") + ylab("") + ylim(-.05,.5) +
  scale_fill_discrete(name="Annotation\nGroup")+
  guides(shape=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                  angle = 45, 
                                  #margin = ggplot2::margin(t = 35),
                                  hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20))

#K562
ggplot(all_rfperfs_mcc[which(all_rfperfs_mcc$CL=="K562"),], aes(x=Resolution, y=MCC, group=Annotation, fill=Annotation)) +
  geom_bar(stat="identity", position = position_dodge()) +
  geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,
                 position=position_dodge(.9), alpha=0.75) +
  theme_minimal() +
  theme_bw()+
  #xlab("") + ylab("") + ylim(-.05,.5) +
  scale_fill_discrete(name="Annotation\nGroup")+
  guides(shape=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                  angle = 45, 
                                  #margin = ggplot2::margin(t = 35),
                                  hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20))
```

>>>>

#GM12878
a <- ggplot(all_rfperfs_mcc[which(all_rfperfs_mcc$CL=="GM12878"),], aes(x=Resolution, y=MCC, group=Annotation, fill=Annotation)) +
  geom_bar(stat="identity", position = position_dodge()) +
  geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,
                 position=position_dodge(.9), alpha=0.75) +
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("MCC") + 
  scale_fill_discrete(name="Annotation Group")+
  ggtitle("GM12878") +
  theme(axis.text.x = element_text(size=15,
                                  angle = 45, 
                                  #margin = ggplot2::margin(t = 35),
                                  hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20))

#K562
b <- ggplot(all_rfperfs_mcc[which(all_rfperfs_mcc$CL=="K562"),], aes(x=Resolution, y=MCC, group=Annotation, fill=Annotation)) +
  geom_bar(stat="identity", position = position_dodge()) +
  geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,
                 position=position_dodge(.9), alpha=0.75) +
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") +
  scale_fill_discrete(name="Annotation\nGroup")+
  ggtitle("K562") +
  theme(axis.text.x = element_text(size=15,
                                  angle = 45, 
                                  #margin = ggplot2::margin(t = 35),
                                  hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20))

figure <- ggarrange(a,b,
                ncol = 2, nrow = 1, 
                common.legend = TRUE, 
                legend = "bottom")
figure
```

# Plots v2

```{r}
ggplot(all_rfperfs_mcc, aes(x=Resolution, y=MCC, group=Annotation, fill=Annotation)) +
  geom_bar(stat="identity", position = position_dodge()) +
  geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,
                 position=position_dodge(.9), alpha=0.75) +
  facet_grid(~ CL) +
  theme_minimal() +
  theme_bw()+
  #xlab("") + ylab("") + ylim(-.05,.5) +
  scale_fill_discrete(name="Annotation Group")+
  guides(shape=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                  angle = 45, 
                                  #margin = ggplot2::margin(t = 35),
                                  hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  strip.text.x = element_text(size = 15),
  panel.spacing = unit(2, "lines"),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20),
  legend.position = "bottom")
```

### 2019-07-01 Scripts/evaluating_variable_importances.Rmd
editted script for figure

```{r}
#GM12878
all_varimps_gm12878 <- cbind.data.frame(varimp_gm12878_10kb$Feature,
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878 <- all_varimps_gm12878[order(rowMeans(all_varimps_gm12878[,-1]), decreasing = TRUE),]
all_varimps_gm12878 <- all_varimps_gm12878[1:20,]
all_varimps_gm12878 <- melt(all_varimps_gm12878)

ggplot(all_varimps_gm12878, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("Resolution") +
  ylab("Transcription Factor") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

#K562
all_varimps_K562 <- cbind.data.frame(varimp_K562_10kb$Feature,
                                        varimp_K562_10kb$aveimp10kb,
                                        varimp_K562_25kb$aveimp25kb,
                                        varimp_K562_50kb$aveimp50kb,
                                        varimp_K562_100kb$aveimp100kb)
names(all_varimps_K562) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_K562 <- all_varimps_K562[order(rowMeans(all_varimps_K562[,-1]), decreasing = TRUE),]
all_varimps_K562 <- all_varimps_K562[1:20,]
all_varimps_K562 <- melt(all_varimps_K562)

ggplot(all_varimps_K562, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("Resolution") +
  ylab("Transcription Factor") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))
```

@@

```{r}
#GM12878
all_varimps_gm12878 <- cbind.data.frame(varimp_gm12878_10kb$Feature,
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878 <- all_varimps_gm12878[order(rowMeans(all_varimps_gm12878[,-1]), decreasing = TRUE),]
#all_varimps_gm12878 <- all_varimps_gm12878[1:20,]
all_varimps_gm12878 <- melt(all_varimps_gm12878)

chromstates_gm12878_plot <- ggplot(all_varimps_gm12878, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

#K562
all_varimps_K562 <- cbind.data.frame(varimp_K562_10kb$Feature,
                                        varimp_K562_10kb$aveimp10kb,
                                        varimp_K562_25kb$aveimp25kb,
                                        varimp_K562_50kb$aveimp50kb,
                                        varimp_K562_100kb$aveimp100kb)
names(all_varimps_K562) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_K562 <- all_varimps_K562[order(rowMeans(all_varimps_K562[,-1]), decreasing = TRUE),]
#all_varimps_K562 <- all_varimps_K562[1:20,]
all_varimps_K562 <- melt(all_varimps_K562)

chromstates_K562_plot <- ggplot(all_varimps_K562, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

figure <- ggarrange(chromstates_gm12878_plot,
                    chromstates_K562_plot,
                ncol = 2, nrow = 1, 
                common.legend = TRUE, 
                legend = "right",
                labels = "AUTO",
                font.label = list(size=20))
figure
annotate_figure(figure,
    bottom = text_grob("Resolution", color = "black", size = 20),
    left = text_grob("Chromatin States", color = "black", rot = 90, size=20)
)

@@

```{r}
#GM12878
all_varimps_gm12878 <- cbind.data.frame(varimp_gm12878_10kb$Feature,
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878 <- all_varimps_gm12878[order(rowMeans(all_varimps_gm12878[,-1]), decreasing = TRUE),]
#all_varimps_gm12878 <- all_varimps_gm12878[1:20,]
all_varimps_gm12878 <- melt(all_varimps_gm12878)

histones_gm12878_plot <- ggplot(all_varimps_gm12878, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

#K562
all_varimps_K562 <- cbind.data.frame(varimp_K562_10kb$Feature,
                                        varimp_K562_10kb$aveimp10kb,
                                        varimp_K562_25kb$aveimp25kb,
                                        varimp_K562_50kb$aveimp50kb,
                                        varimp_K562_100kb$aveimp100kb)
names(all_varimps_K562) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_K562 <- all_varimps_K562[order(rowMeans(all_varimps_K562[,-1]), decreasing = TRUE),]
#all_varimps_K562 <- all_varimps_K562[1:20,]
all_varimps_K562 <- melt(all_varimps_K562)

histones_K562_plot <- ggplot(all_varimps_K562, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

figure <- ggarrange(histones_gm12878_plot,
                    histones_K562_plot,
                ncol = 2, nrow = 1, 
                common.legend = TRUE, 
                legend = "right",
                labels = "AUTO",
                font.label = list(size=20))
figure
annotate_figure(figure,
    bottom = text_grob("Resolution", color = "black", size = 20),
    left = text_grob("Histone Modifications", color = "black", rot = 90, size=20)
)

>>>>

```{r}
#GM12878
all_varimps_gm12878_tfbs <- cbind.data.frame(varimp_gm12878_10kb$Feature,
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878_tfbs) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878_tfbs <- all_varimps_gm12878_tfbs[order(rowMeans(all_varimps_gm12878_tfbs[,-1]), decreasing = TRUE),]
all_varimps_gm12878_tfbs <- all_varimps_gm12878_tfbs[1:20,]
all_varimps_gm12878_tfbs <- melt(all_varimps_gm12878_tfbs)

a <- ggplot(all_varimps_gm12878_tfbs, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("Transcription Factor") +
  ggtitle("GM12878") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size = 20))

#K562
all_varimps_K562_tfbs <- cbind.data.frame(varimp_K562_10kb$Feature,
                                        varimp_K562_10kb$aveimp10kb,
                                        varimp_K562_25kb$aveimp25kb,
                                        varimp_K562_50kb$aveimp50kb,
                                        varimp_K562_100kb$aveimp100kb)
names(all_varimps_K562_tfbs) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_K562_tfbs <- all_varimps_K562_tfbs[order(rowMeans(all_varimps_K562_tfbs[,-1]), decreasing = TRUE),]
all_varimps_K562_tfbs <- all_varimps_K562_tfbs[1:20,]
all_varimps_K562_tfbs <- melt(all_varimps_K562_tfbs)

b <- ggplot(all_varimps_K562_tfbs, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("") +
  ggtitle("K562") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "lightblue",
                      midpoint = 50,
                      high = muted("blue"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size = 20))

figure <- ggarrange(a,b,
                ncol = 2, nrow = 1, 
                common.legend = TRUE, 
                legend = "bottom")
figure

@@

```{r}
#GM12878
all_varimps_gm12878_chromstates <- cbind.data.frame(varimp_gm12878_10kb$Feature,
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878_chromstates) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878_chromstates <- all_varimps_gm12878_chromstates[order(rowMeans(all_varimps_gm12878_chromstates[,-1]), decreasing = TRUE),]
#all_varimps_gm12878_chromstates <- all_varimps_gm12878_chromstates[1:20,]
all_varimps_gm12878_chromstates <- melt(all_varimps_gm12878_chromstates)

a <- ggplot(all_varimps_gm12878_chromstates, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("Chromatin State") +
  ggtitle("GM12878") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size = 20))

#K562
all_varimps_K562_chromstates <- cbind.data.frame(varimp_K562_10kb$Feature,
                                        varimp_K562_10kb$aveimp10kb,
                                        varimp_K562_25kb$aveimp25kb,
                                        varimp_K562_50kb$aveimp50kb,
                                        varimp_K562_100kb$aveimp100kb)
names(all_varimps_K562_chromstates) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_K562_chromstates <- all_varimps_K562_chromstates[order(rowMeans(all_varimps_K562_chromstates[,-1]), decreasing = TRUE),]
#all_varimps_K562_chromstates <- all_varimps_K562_chromstates[1:20,]
all_varimps_K562_chromstates <- melt(all_varimps_K562_chromstates)

b <- ggplot(all_varimps_K562_chromstates, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("") +
  ggtitle("K562") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "lightblue",
                      midpoint = 50,
                      high = muted("blue"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size = 20))

figure <- ggarrange(a,b,
                ncol = 2, nrow = 1, 
                common.legend = TRUE, 
                legend = "bottom")
figure
```

@@

```{r}
#GM12878
all_varimps_gm12878_histones <- cbind.data.frame(varimp_gm12878_10kb$Feature,
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878_histones) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878_histones <- all_varimps_gm12878_histones[order(rowMeans(all_varimps_gm12878_histones[,-1]), decreasing = TRUE),]
#all_varimps_gm12878_histones <- all_varimps_gm12878_histones[1:20,]
all_varimps_gm12878_histones <- melt(all_varimps_gm12878_histones)

a2 <- ggplot(all_varimps_gm12878_histones, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("Histone Modification") +
  ggtitle("GM12878") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size = 20))

#K562
all_varimps_K562_histones <- cbind.data.frame(varimp_K562_10kb$Feature,
                                        varimp_K562_10kb$aveimp10kb,
                                        varimp_K562_25kb$aveimp25kb,
                                        varimp_K562_50kb$aveimp50kb,
                                        varimp_K562_100kb$aveimp100kb)
names(all_varimps_K562_histones) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_K562_histones <- all_varimps_K562_histones[order(rowMeans(all_varimps_K562_histones[,-1]), decreasing = TRUE),]
#all_varimps_K562_histones <- all_varimps_K562_histones[1:20,]
all_varimps_K562_histones <- melt(all_varimps_K562_histones)

b2 <- ggplot(all_varimps_K562_histones, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("") +
  ggtitle("K562") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "lightblue",
                      midpoint = 50,
                      high = muted("blue"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size = 20))

figure <- ggarrange(a,b,
                ncol = 2, nrow = 1, 
                common.legend = TRUE, 
                legend = "bottom")
figure

figure <- ggarrange(a,b,a2,b2,
                ncol = 2, nrow = 2, 
                common.legend = TRUE, 
                legend = "bottom",
                labels = c("A","","B",""),
                font.label = list(size=25))
figure
```

### 2019-07-01 Scripts/proportion_of_importance_per_annotation.Rmd
editted script for figure

ggplot(all_propimp_gm12878_summ, aes(fill=Annotation, y=Prop.VI, x=Resolution)) + 
  geom_bar( stat="identity", position="fill") +
  xlab("Resolution") +
  ylab("Proportion of Importance") +
  scale_fill_discrete(name="Annotation\nGroup")+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

@@

ggplot(all_propimp_K562_summ, aes(fill=Annotation, y=Prop.VI, x=Resolution)) + 
  geom_bar( stat="identity", position="fill") +
  xlab("Resolution") +
  ylab("Proportion of Importance") +
  scale_fill_discrete(name="Annotation\nGroup")+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

@@

>>>>

a <- ggplot(all_propimp_gm12878_summ, aes(fill=Annotation, y=Prop.VI, x=Resolution)) + 
  geom_bar( stat="identity", position="fill") +
  xlab("") +
  ylab("Proportion of Importance") +
  scale_fill_discrete(name="Annotation Group")+
  ggtitle("GM12878") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20))

@@

b <- ggplot(all_propimp_K562_summ, aes(fill=Annotation, y=Prop.VI, x=Resolution)) + 
  geom_bar( stat="identity", position="fill") +
  xlab("") +
  ylab("") +
  scale_fill_discrete(name="Annotation Group")+
  ggtitle("K562") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20))

@@

# Plots v2

```{r}
figure <- ggarrange(a,b,
                ncol = 2, nrow = 1, 
                common.legend = TRUE, 
                legend = "bottom")
figure

all_propimp <- rbind(all_propimp_gm12878_summ, all_propimp_K562_summ)
all_propimp$CL <- c(rep("GM12878", 12),
                    rep("K562", 12))

ggplot(all_propimp, aes(fill=Annotation, y=Prop.VI, x=Resolution)) + 
  geom_bar( stat="identity", position="fill") +
  facet_grid(~ CL) +
  xlab("Resolution") +
  ylab("Proportion of Importance") +
  scale_fill_discrete(name="Annotation Group")+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 15),
        panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        legend.position = "bottom")
